Automatic Identification and Annotation of Tasks in Structured Programs

### 2018-01-20 docs/ACM/paper.tex
Adding first definitions.

\title[Automatic Identification and Annotation of Parallel Tasks in Structured
Programs]
{Automatic Identification and Annotation of Parallel Tasks in Structured Programs}

@@

\begin{figure}[t!]
\begin{center}
\includegraphics[width=1\columnwidth]{images/alg_main}
\caption{The main steps of our code generator.}
\label{fig:alg_main}
\end{center}
\end{figure}

@@

\begin{figure}[t!]
\begin{center}
\includegraphics[width=1\columnwidth]{images/expand_alg}
\caption{Discovery of tasks via expansion of hammock regions.}
\label{fig:expand_alg}
\end{center}
\end{figure}

>>>>

\title[Automatic Identification and Annotation of Tasks in Structured
Programs]
{Automatic Identification and Annotation of Tasks in Structured Programs}

@@

Figure~\ref{fig:alg_main} provides a high-level view of a source-to-source
compiler that incorporates the techniques discussed in this paper.
This pseudo-code uses several concepts well-known in the compiler's
literature, such as control flow graphs~\cite{Kildall73} and
dependence graphs~\cite{Ferrante87}.
We built on top of such concepts, as well as others, like
symbolic range analysis~\cite{Blume94}, and natural loops~\cite{Allen70}.
In the rest of this section we explain how we have combined this previous
knowledge in order to delimit and annotate tasks in structured programs.
Our presentation focus on the new elements that we had to add onto known
techniques, in order to adapt them to our purposes.

\begin{figure}[h]
\begin{center}
\includegraphics[width=1\columnwidth]{images/alg_main}
\caption{The main steps of our code generator.}
\label{fig:alg_main}
\end{center}
\end{figure}

\paragraph{The syntax that we handle.}
Our goal is to identify {\em tasks} in {\em structured} programs.
Definition~\ref{def:task} formalizes the notion of task.
A structured program is a program that can be partitioned in {\em hammock
regions}, a concept introduced by Ferrante {\em et al.}~\cite{Ferrante87} in
the middle 80's.
The structure of this program is described by a a Control Flow Graph $G$ --
a directed graph with a starting node $s$, and an exit node $x$.
A hammock region is a subgraph $G' \subseteq G$, with a special node
$h$, which {\em dominates}\footnote{A node $n_1 \in G$ dominates another node
$n_2 \in G$ if every path from  $S$ to $n_2$ goes across $n_1$.
Inversely, $n_1$ post-dominates $n_2$ if every path from $n_2$ to $x$ must
go across $n_1$.} every other node in $G'$.
Additionally, there exists a node $w \in G$, $w \notin G'$, such that
$w$ {\em post-dominates} every node in $G'$.
In this definition, $h$ is the {\em entry point}, and $w$ is the {\em exit point}
of $G'$.

\begin{definition}[Task]
\label{def:task}
Given a program $P$, a task $T$ is a tuple $(G', M)$ formed by a hammock region
$G'$, plus a set $M$ of memory regions that represent the dependences of $T$.
\end{definition}

Definition~\ref{def:task} uses the concept of {\em memory region}.
Syntactically, memory regions are described by program variables and/or pointers
plus ranges of offsets that these pointers are allowed to dereference.
If a task $(T_1, M_1)$ writes onto a memory region $m$, and task
$(T_2, M_2)$ contains code that reads $m$, then $m \in M_1$, to ensure that
dependences are respected.
If a program $P$ is partitioned into a set of $n$ tasks $\{(T_1, M_1),
\ldots (T_n, M_n)\}$, then this partition is said to be {\em correct} if any
topological ordering of the tasks, as determined by dependence relations, always
leads to the same results as the sequential execution of $P$.

\paragraph{The annotations that we use.}

@@

\begin{figure}[t!]
\begin{center}
\includegraphics[width=1\columnwidth]{images/expand_alg}
\caption{Task discovery via expansion of hammock regions.}
\label{fig:expand_alg}
\end{center}
\end{figure}
